An Open Repository of Real-Time COVID-19 Indicators

### 2021-09-23 indicators/paper/responses-to-reviews.tex

\title{Response to peer reviews}
\author{}
\date{\today}

\begin{document}
\maketitle

\section*{Editor}

\begin{quote}
  The reviewers both saw high value in the database and regarded the paper as
  important and relevant. Reviewer 2 had several high-level comments about the
  current framing of the results and offered a number of suggestions for the
  authors to consider additional or modified analyses that would strengthen the
  paper. I would like to invite the authors to submit a revised version of the
  manuscript including a detailed point-by-point response to the reviewer
  comments, particularly where Reviewer 2 has suggested need for either further
  analyses or pointed to notable limitations. While the authors should use their
  discretion regarding whether additional analyses would be within scope for the
  revision, it will be important to respond to the suggestions in either case
  and at least to expand on limitations as relevant in the revised manuscript.
\end{quote}
We thank the editor and reviewers for their comments and the opportunity to make
revisions. We have made a number of revisions, described in detail below; in
summary, these revisions include:
\begin{itemize}
\item Additional graphics in the Supplementary Information, and additional
  references to it where appropriate, to provide additional useful ways to view
  the data and comparisons to outcomes other than COVID-19 cases

\item Clarification of limitations, both in our data and in other publicly
  available data sources, so the strengths and weaknesses of our data compared
  to other sources are clearer

\item Improved analyses in the Results section, including more pertinent figures
  and clearer examples.
\end{itemize}
We believe these changes have strengthened the manuscript, and describe them in
more detail below.

@@

We have chosen not to include additional descriptive statistics or comparisons
between signals for two reasons. First, given the large number of signals
available in our API, a table of descriptive statistics would be prohibitively
large; this is particularly difficult if one accounts for time and geography by
presenting statistics over time or across space. Second, it's not clear to us
what a reader would gain from such statistics. Because the data is freely
available, a reader interested in any specific signal can quickly investigate it
and explore whatever aspects of it are of interest.

Our Supplementary Information does include additional exploratory analyses of
the signals, including state- and county-level time series plots that reveal
interesting signal behavior.

### 2021-09-23 indicators/paper/paper.tex
Plot location, summary of review responses

Altogether, we collect 110 signals from 12 distinct sources, aggregate and
process them, and provide them in a common format for public access. This
unifies both unique (not available anywhere else) and standard COVID data
streams into a single common format, enabling efficient comparison and modeling.
A summary of the data sources and signals in the API is in
Table~\ref{tab:sources_signals}, and detailed documentation is available at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how
CTIS results in January 2021, based on an item asking survey respondents whether
they would accept a COVID-19 vaccine if one were vaccinated today, predicted
actual uptake of COVID-19 vaccines by July 2021. It also illustrates a
geographical disparity: in the Northeast, actual vaccination rates more closely
match vaccine acceptance in January than they do in the South, where vaccination
rates lag overall. While these results must be interpreted carefully due to
potential sampling biases in the survey, they illustrate the potential of data
in the COVIDcast API to inform public health decision-making.

>>>>

% TODO Recount!
Altogether, we collect 110 signals from 12 distinct sources, aggregate and
process them, and provide them in a common format for public access. This
unifies both unique (not available anywhere else) and standard COVID data
streams into a single common format, enabling efficient comparison and modeling.
A summary of the data sources and signals in the API is in
Table~\ref{tab:sources_signals}, and detailed documentation is available at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how CTIS
results in January 2021, based on an item asking survey respondents whether they
would accept a COVID-19 vaccine if one were vaccinated today, predicted actual
uptake of COVID-19 vaccines by July 2021 (as reported by the Centers for Disease
Control and Prevention). It also illustrates a geographical disparity: in the
Northeast, actual vaccination rates more closely match vaccine acceptance in
January than they do in the South, where vaccination rates lag overall. While
these results must be interpreted carefully due to potential sampling biases in
the survey, they illustrate the potential of data in the COVIDcast API to inform
public health decision-making.
